tesis

### 2020-05-28 production/prod_analisis.rmd
Version seminario de grado
Entrega 1

```{r}
iccssimce <- read_dta("iccs_simce.dta")
```

@@

@@

screenreg(list(results_1,results_2,results_3, results_4, results_5 ), type="text")

@@

@@

save(int1, file= "imagenes/int1.png")
save(int2, file= "imagenes/int2.png")
save(intcentrada, file= "imagenes/int3.png")
int1
int2
intcentrada

@@

cor <- cor(basecor)
Correlaciones  <-corrplot.mixed(cor)
save(Correlaciones, file = "imagenes/correlaciones.html")

@@

save(regresion, file = "imagenes/reg.png")

>>>>

```{r}
iccssimce <- read_dta("../input/data/original/iccs_simce.dta")
```

@@

```{r results='asis'}

@@

save(results_1, file = "../output/images/results_1.Rdata")
save(results_2, file = "../output/images/results_2.Rdata")
save(results_3, file = "../output/images/results_3.Rdata")
save(results_4, file = "../output/images/results_4.Rdata")
save(results_5, file = "../output/images/results_5.Rdata")

regresion_tex <-texreg(list(results_1,results_2,results_3, results_4, results_5 ))
regresion_html <-htmlreg(list(results_1,results_2,results_3, results_4, results_5 ))

save(regresion_tex, file = "../output/images/regtex.Rdata")
save(regresion_tex, file = "../output/images/reghtml.Rdata")

load(file = "../output/images/reghtml.Rdata")

@@

save(results_7, file = "../output/images/results_7.Rdata")
save(results_8, file = "../output/images/results_8.Rdata")

@@

save(int1, file= "../output/images/int1.png")
save(int2, file= "../output/images/int2.png")
save(intcentrada, file= "../output/images/int3.png")
int1
int2
intcentrada

@@

cor <- cor(basecor)
Correlaciones  <-corrplot.mixed(cor)
save(Correlaciones, file = "../output/images/correlaciones.html")

@@

save(results_5, file = "../output/images/results_5.Rdata")
